Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-16 paper.tex
chore: more on notation

  Sample a batch of graph transitions $(G^i_o,G^i_a,G^i_r,G^i_o)$ 
   from $\mathcal{D}$ and merge them in $(G_o,G_a,G_r,G_o)$; \lukas{how does the merge work? do we explain this?}

  Compute the target Q-value for each node in the graph: 
  $y = G_r + \gamma * \max{a'} Q(s'i,a';\theta^{-})$;

>>>>

  Sample a batch of graph transitions $(G^i_o,G^i_a,G^i_r,G'^i_o)$ 
   from $\mathcal{D}$ and merge them in $(G^b_o,G^b_a,G^b_r,G'^b_o)$; \lukas{how does the merge work? do we explain this?}

  Compute the target Q-value for each node $v$ in the graph $G$: 
  $y = G^b_r + \gamma * \max{a'} Q(o'i,a';\theta^{-})$;
